---
title: "check_correlations.Rmd"
author: "Erika"
date: "4/27/2020"
output: html_document
---

Looking at methods for multiple regression modeling for Kate's camera trap data.

set up the workspace
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(Hmisc)
library(corrplot)
library(ggcorrplot)

```
Load the draft data
```{r}
LS<-read.csv("/Users/ebar/Dropbox/1Courses/ResearchGroup/2019-2020/Leslie/SYEvariables.csv")
```

### Leslie's data
Columns 1 - 2 identify the different forests and plots and are not quantitative variables. 

Let's make a DF of the possible **numeric predictor** variables to look for correlations

```{r}
Lvars<-LS[, 3:27]
Lvars<-dplyr::select(Lvars, - Forest_type)
```
Now remove response variables from Lvars
```{r}
LPreds<-Lvars[,5:24]
```
Two variables, Lakes_500 and Residential_1km are 0, so remove those
```{r}
LPreds<-select(LPreds, -c(Lakes_500, Residential_1km))
```

Now I need a correlation matrix of the variables

```{r}
cor_tests<-cor(LPreds, method = "pearson", use = "complete.obs")
cor_tests<-round(cor_tests, 2)
```
Now to get p-values, need hmisc package
```{r}
Lresult<-rcorr(as.matrix(LPreds)) #rcorr is a hmisc function

```
Now flatten to get easier to understand results
```{r}
flattenCorrMatrix<-function(cormat,pmat){
  ut<-upper.tri(cormat)
  data.frame(
    row = rownames (cormat)[row(cormat) [ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor = (cormat)[ut],
    p = pmat[ut]
  )
}
```
Now use
```{r}
Lres_tab<-flattenCorrMatrix(Lresult$r, Lresult$P)
Lhigh_cor<-filter(Lres_tab, cor >= 0.7 | cor <= -0.7 )
```
#### Now Visualize

Draw a correlogram with corrplot package

```{r}
corrplot(cor_tests, type = "lower", order = "hclust", tl.col = "black", tl.srt = 45)
```
Use ggcorrplot
http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2

```{r}
ggcorrplot(Lresult$r, hc.order = TRUE, type = "lower", lab = TRUE, outline.col = "white", p.mat = Lresult$P, insig = "blank" )
```
Remove the following variables and then write file for regression.
* Deciduous_1km
* Mixed 1km
* Evergreen 1 km
* Cropland 1km
* wetland 1 km
* cropland 500 m
* wetland 500 m

```{r}
remove<-c("Cropland_500", "Wetland_500", "Deciduous_1km", "MixedForest_1km", "Evergreen_1km", "Cropland_1km", "Wetland_1km")
LS<-dplyr::select(LS, -remove)
```
Now write file

```{r}
write.csv(LS, "Data/LSmodel.csv")
```


Use ggcorrplot
http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2

```{r}
ggcorrplot(Lresult$r, hc.order = TRUE, type = "lower", lab = TRUE, outline.col = "white", p.mat = Lresult$P, insig = "blank" )
```

