---
title: "check_correlations.Rmd"
author: "Erika"
date: "4/27/2020"
output: html_document
---

Looking at methods for multiple regression modeling for Kate's camera trap data.

set up the workspace
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(Hmisc)
library(corrplot)
library(ggcorrplot)

```
Load the draft data
```{r}
KA<-read.csv("/Users/ebar/Dropbox/1Courses/ResearchGroup/2019-2020/Kate Andy/Covariates_draft2.csv")

LS<-read.csv("/Users/ebar/Dropbox/1Courses/ResearchGroup/2019-2020/Leslie/SYEvariables.csv")
```

### Kate's data
Columns 1 - 3 identify the different cameras and are not predictor variables. 

Let's make a DF of the possible **numeric predictor** variables to look for correlations

```{r}
K_cont_vars<-names(KA)
remove<-c("Camera", "SD_Card", "Round","ForestType", "Forest","Season", "Cam_Model")
K_cont_vars<-K_cont_vars[!K_cont_vars %in% remove]

KCPreds<-KA %>% select(all_of(K_cont_vars))
```
Now I need a correlation matrix of the variables

```{r}
cor_tests<-cor(KCPreds, method = "pearson", use = "complete.obs")
cor_tests<-round(cor_tests, 2)
```
Now to get p-values, need hmisc package
```{r}
Kresult<-rcorr(as.matrix(KCPreds)) #rcorr is a hmisc function

```
Now flatten to get easier to understand results
```{r}
flattenCorrMatrix<-function(cormat,pmat){
  ut<-upper.tri(cormat)
  data.frame(
    row = rownames (cormat)[row(cormat) [ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor = (cormat)[ut],
    p = pmat[ut]
  )
}
```
Now use
```{r}
Kres_tab<-flattenCorrMatrix(Kresult$r, Kresult$P)
Khigh_cor<-filter(Kres_tab, cor >= 0.7 | cor <= -0.7 )
```
According to Khigh_cor, diversity indices are correlated, but we don't care since we won't be using them as predictors.  P_Evergreen50 is highly correlated with P_Deciduous50 and P_Evergreen100 with P_Deciduous100 so we'll just keep one of those for each (how about P_Deciduous).  P_Forest100 is highly correlated with P_Wetland100 so dump P_Wetland100.  Finally, Keep Forest_Density and Forest_Dominance as the tree and sapling densities and tree dominance are highly corrleated.  So keep sapling dominance, but not tree dominance, and get rid of both tree and sapling density.

List of variables to remove from predictors
```{r}
correlated<-c("P_Evergreen50", "P_Evergreen100", "P_Wetland100","Tree_Density", "Sap_Density", "Tree_Dominance")
```
Now write a new KA that omits these variables for use in modeling.

```{r}
KAmodel<-select(KA, -correlated)
write.csv(KAmodel, "Data/KAmodel.csv")
```


#### Now Visualize

Draw a correlogram with corrplot package

```{r}
corrplot(cor_tests, type = "lower", order = "hclust", tl.col = "black", tl.srt = 45)
```
Use ggcorrplot
http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2

```{r}
ggcorrplot(Kresult$r, hc.order = TRUE, type = "lower", lab = TRUE, outline.col = "white", p.mat = Kresult$P, insig = "blank" )
```



